---
title: "Week 11 Challenge"
output: html_notebook
---

API Link: <https://api.covidactnow.org/v2/states.timeseries.json?apiKey=af425098c233446aa11a347a9dbd4d6a>

```{r}
library(httr)
library(jsonlite)
library(tidyverse)
```

```{r}
historic_state_data_url <- "https://api.covidactnow.org/v2/states.timeseries.json?apiKey=af425098c233446aa11a347a9dbd4d6a"

raw_data <- GET(historic_state_data_url)
```

##Step2: Extracting data

1.  json format to data-frame

```{r}
data <- fromJSON(rawToChar(raw_data$content))
```

##Step3: Exploring data

```{r}
glimpse(data)
```

##Step5: Mapping Variables to Questions

```{r}
time_series <- data %>% unnest(actualsTimeseries)
actuals_unnested <- data %>% unnest(actuals)
metrics_unnested <- data %>% unnest(metrics)
```

##Step5.5: Answers to Questions a. i. What is the population in various states of U.S.A

```{r}
data %>% select(state, population)
```

ii. What fraction of the population was infected?

```{r}
sum(actuals_unnested$cases) / sum(data$population)
```

iii. What fraction of infected persons recovered ?

```{r}
n_recovered <- sum(actuals_unnested$cases) - sum(actuals_unnested$deaths)
percent_recovered <- n_recovered / sum(actuals_unnested$cases)
percent_recovered
```

iv. What fraction of the population is currently vaccinated?

```{r}
mean(metrics_unnested$vaccinationsCompletedRatio, na.rm = TRUE)
```

v.  What was the transmission like in the various states?

```{r}
data %>% select(state, cdcTransmissionLevel)
```

```{r}
time_series_transmission <- tibble(Date=time_series$cdcTransmissionLevelTimeseries[[which(data$state=="CA")]]$date)

time_series_transmission$Alaska <- time_series$cdcTransmissionLevelTimeseries[[which(data$state=="AK")]]$cdcTransmissionLevel

time_series_transmission$California <- time_series$cdcTransmissionLevelTimeseries[[which(data$state=="CA")]]$cdcTransmissionLevel

time_series_transmission$New_Jersey <- time_series$cdcTransmissionLevelTimeseries[[which(data$state=="NJ")]]$cdcTransmissionLevel

time_series_transmission$Tennessee <- time_series$cdcTransmissionLevelTimeseries[[which(data$state=="TN")]]$cdcTransmissionLevel

time_series_transmission$District_of_Columbia <- time_series$cdcTransmissionLevelTimeseries[[which(data$state=="DC")]]$cdcTransmissionLevel

print(head(time_series_transmission))
```

vi\. How did the disease progress since it started ?

```{r}
# New data-frame with dates
time_series_cases <- list(Alaska = time_series %>% filter(state=="AK") %>% select(date,cases))
# Cases of each state
time_series_cases$California <- time_series %>% filter(state=="CA") %>% select(date,cases)
time_series_cases$New_Jersey <- time_series %>% filter(state=="NJ") %>% select(date,cases)
time_series_cases$Tennessee <- time_series %>% filter(state=="TN") %>% select(date,cases)
time_series_cases$District_of_Columbia <- time_series %>% filter(state=="DC") %>% select(date,cases)
```

##Step6: Analysing Data
i.

```{r}
ggplot(data, aes(x=state,y=population)) + geom_bar(stat="identity") +labs(x="States",y="Population") + theme_bw()
```

ii. 
```{r}
ggplot(data, aes(x=state,y=(data$actuals$cases/population))) + geom_bar(stat="identity") + labs(x="States",y="Infected (%)")+theme_bw()

```

iii.
```{r}
ggplot(data, aes(x=state,y=((data$actuals$cases - data$actuals$deaths)/population))) + geom_bar(stat="identity") + labs(x="States",y="Recovered (%)")+theme_bw()
```
iv. 
```{r}
ggplot(metrics_unnested, aes(x=state,y=metrics_unnested$vaccinationsCompletedRatio)) + geom_bar(stat="identity") + labs(x="States",y="Recovered (%)")+theme_bw()
```

v.
```{r}
time_series_transmission[seq(1,1300,by=100),]%>%
pivot_longer(cols=Alaska:District_of_Columbia,names_to="Countries",values_to="Transmission") %>%
ggplot(aes(x=Date,y=Transmission,colour=Countries,group=Countries)) +
geom_point(show.legend=TRUE) + labs(x="Date",y="Transmission Level")+theme_bw()
```

vi.
```{r}
data_to_plot <- tibble(Date_Alaska = time_series_cases$Alaska$date[seq(1,1300,by=100)],
Cases_Alaska = time_series_cases$Alaska$cases[seq(1,1300,by=100)],
Date_California = time_series_cases$California$date[seq(1,1300,by=100)],
Cases_California = time_series_cases$California$cases[seq(1,1300,by=100)],
Date_New_Jersey = time_series_cases$New_Jersey$date[seq(1,1300,by=100)],
Cases_New_Jersey = time_series_cases$New_Jersey$cases[seq(1,1300,by=100)],
Date_Tennessee = time_series_cases$Tennessee$date[seq(1,1300,by=100)],
Cases_Tennessee = time_series_cases$Tennessee$cases[seq(1,1300,by=100)],
Date_District_of_Columbia = time_series_cases$District_of_Columbia$date[seq(1,1300,by=100)],
Cases_District_of_Columbia = time_series_cases$District_of_Columbia$cases[seq(1,1300,by=100)])
data_to_plot
```

```{r}
install.packages("cowplot")
library(cowplot)
```
```{r}
fig1<- ggplot(data_to_plot, aes(x=Date_Alaska,y=Cases_Alaska)) +
geom_point() + labs(x="Date",y="Cases", title="Alaska") + theme_bw()
fig2<- ggplot(data_to_plot, aes(x=Date_California,y=Cases_California)) +
geom_point() + labs(x="Date",y="Cases", title="California") + theme_bw()
fig3<- ggplot(data_to_plot, aes(x=Date_New_Jersey,y=Cases_New_Jersey)) +
geom_point() + labs(x="Date",y="Cases", title="New Jersey") + theme_bw()
fig4<- ggplot(data_to_plot, aes(x=Date_Tennessee,y=Cases_Tennessee)) +
geom_point() + labs(x="Date",y="Cases", title="Tennessee") + theme_bw()
fig5<- ggplot(data_to_plot, aes(x=Date_District_of_Columbia,y=Cases_District_of_Columbia)) +
geom_point() + labs(x="Date",y="Cases", title="District of Columbia") + theme_bw()
plot_grid(fig1 + theme(legend.justification = c(0,1)),
fig2 + theme(legend.justification = c(1,0)),
fig3 + theme(legend.justification = c(0,1)),
fig4 + theme(legend.justification = c(1,0)),
fig5 + theme(legend.justification = c(0,1)),
align = "v", axis = "lr", nrow=3,
ncol = 2,labels = LETTERS[1:5],
rel_heights = c(1,2))
```

