---
pdf_document: default
author: "Nicole Lim"
date: "`r Sys.Date()`"
output:
  html_document: null
  df_print: paged
  pdf_document: default
title: "Week-4: Code-along"
---

  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# II. Code to edit and execute using the Code-along.Rmd file 
<br>

## A. Data Wrangling
<br>

### 1. Loading packages (Slide #16)

```{r, eval=TRUE,echo=TRUE, message = FALSE}
# Load package tidyverse
library(tidyverse)
```

### 2. Loading data-set (Slide #16)

```{r, eval=TRUE,echo=TRUE}
# Read data from the hotels.csv file and assign it to a variable named, "hotels"
hotels <- read_csv("hotels.csv")
```

### 3. List names of the variables in the data-set (Slide #19)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
names(hotels)
```


### 4. Glimpse of contents of the data-set (Slide #20)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
glimpse(hotels)
```
<br>

## B. Choosing rows or columns
<br>

### 5. Select a single column (Slide #24)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
select(hotels, hotel)
```

### 6. Select multiple columns (Slide #25)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
select(hotels, customer_type, is_repeated_guest)
```

### 7. Arrange entries of a column (Slide #28)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
arrange(hotels,lead_time)
```

### 8. Arrange entries of a column in the descending order (Slide #30)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
arrange(hotels, desc(lead_time))
```

### 9. Select columns and arrange the entries of a column (Slide #31)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
arrange( select(hotels, total_of_special_requests), desc(total_of_special_requests)) 
```

### 10. Select columns and arrange the entries of a column using the pipe operator (Slide #37)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% select(lead_time) %>% arrange(desc(lead_time))
```

### 11. Pick rows matching a condition (Slide #44)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
#hotels %>% select(lead_time) %>% filter(lead_time > 300)
hotels %>% filter(children >=1) %>% select(hotel, children)
```

### 12. Pick rows matching multiple conditions (Slide #46)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% filter(children >=1, hotel == "City Hotel") %>% select(hotel, children)
```

### 13. Non-conditional selection of rows: sequence of indices (Slide #49)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
#Slice for selecting rows by their row numbers
hotels %>% slice(1:5)
```

### 14. Non-conditional selection of rows: non-consecutive/specific indices (Slide #50)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% slice(1,2,7)
```

### 15. Pick unique rows using distinct() (Slide #52)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
# distinct(): Creates data with one column, listing the distinct values
hotels %>% distinct(hotel)

```
<br>

## C. Creating new columns
<br>

### 16. Creating a single column with mutate() (Slide #56)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% mutate(teeny_tinies = children + babies) %>% select(hotel, teeny_tinies, children, babies) %>% arrange(desc(teeny_tinies))
```

### 17. Creating multiple columns with mutate() (Slide #58)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% mutate(teeny_tinies = children + babies, avg_teeny_tinies = mean(teeny_tinies)) %>% select(hotel, teeny_tinies, avg_teeny_tinies, children, babies) %>% arrange(desc(teeny_tinies))

hotels %>% select(children, babies) %>% anyNA()
```
<br>

## D. More operations with examples
<br>

### 18. count() to get frequencies (Slide #60)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% count(market_segment)
```

### 19. count() to get frequencies with sorting of count (Slide #61)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% count(market_segment, sort = TRUE)
```

### 20. count() multiple variables (Slide #62)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
#Counts the specific pairs
hotels %>% count (hotel, market_segment)
```

### 21. summarise() for summary statistics (Slide #63)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
#Summarise() collapses the dataframe down to a single summary statistic making a new DF
hotels %>% summarise(mean_adr = mean(adr))
```

### 22. summarise() by using group_by to find mean (Slide #64)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
#Group_by groups a row by its distinct values, good for comparison
hotels %>% group_by(hotel) %>% summarise(mean_adr = mean(adr))
```

### 23. summarise() by using group_by to get count (Slide #65)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
#using Summarise() and n() [which counts grp size] on groupby to count for distinct groups. equivalent to count(column_name)
?n
hotels %>% group_by(hotel) %>% summarise(count = n())

```

### 24. summarise() for multiple summary statistics (Slide #67)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% summarise( min_adr = min(adr), mean_adr = mean(adr), median_adr = median(adr), max_adr = max(adr))

```

### 25. select(), slice() and arrange() (Slide #68)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% select(hotel, lead_time) %>% slice (1:5) %>% arrange(lead_time)
```

### 26. select(), arrange() and slice() (Slide #69)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% select (hotel, lead_time) %>% arrange (desc(lead_time)) %>% slice(1:5)
```

### 27. filter() to select rows based on conditions (Slide #73)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% filter (hotel=="City Hotel")
hotels %>% filter(adults == 0, children >= 1) %>% select(adults, babies, children)

```

### 28. filter() to select rows based on complicated conditions (Slide #74)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% filter(adults == 0, children >= 1 | babies >= 1) %>% select(adults, babies, children)
```

### 29. count() and arrange() (Slide #76)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% count(market_segment) %>% arrange(desc(n))
```

### 30. mutate(), select() and arrange() (Slide #77)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% mutate(teeny_tinies = children + babies) %>% select(children, babies, teeny_tinies) %>% arrange(desc(teeny_tinies))
```


### 31. mutate(), filter() and select() (Slide #78)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
hotels %>% mutate(teeny_tinies = children + babies) %>% filter(teeny_tinies >= 1, hotel == "City Hotel") %>% select(hotel, teeny_tinies) 
```