---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
all_data <- read_csv("kpop_idol_followers.csv")
data <- read_csv("kpop_idol_followers.csv")
#data <- data %>% select(ig_name, Followers)
#glimpse(data)

```

```{r}
ggplot(data, aes(x = Followers)) + geom_boxplot()
```

```{r}
quartiles <- quantile(data$Followers, probs = c( 0.25, 0.75 ))

iqr <- IQR(data$Followers)

lower_outliers <- quartiles[1] - 1.5*iqr
upper_outliers <- quartiles[2] + 1.5*iqr

data_cleaned <- filter(data, data$Followers < upper_outliers)
all_data_cleaned <- filter(all_data, all_data$Followers < upper_outliers)

glimpse(data_cleaned)
```

```{r}
data_length <- data_cleaned %>% mutate( length = nchar(ig_name) )

ggplot (data_length) +
  aes ( y = Followers, 
        x = length) +
  geom_point()

#data_length_classified <- data_length %>% mutate( short = length < 8, medium = 8 < length & length < 16, long = length > 15)

data_length$categories <- cut(data_length$length, breaks=c(seq(0,25,by=8)), labels=c("short", "medium", "long"))


ggplot (data_length) +
  aes ( y = Followers, 
        x = length) +
  geom_point() +
  facet_wrap(~ categories)

ggplot(data_length) + 
  aes (x = Followers, 
      fill = categories) +
  geom_histogram()



```

```{r}
medians_of_length_categories <- tibble(
  short_median = median(filter(data_length, categories == "short")$Followers),
  medium_median = median(filter(data_length, categories == "medium")$Followers),
  long_median = median(filter(data_length, categories == "long")$Followers))
```

```{r}
library(stringr)
data_underscore <- data_cleaned %>% mutate(number_of_underscores = str_count(data_cleaned$ig_name, "_"))

ggplot (data_underscore) +
  aes ( y = Followers, 
        x = number_of_underscores) +
  geom_point()
```

```{r}
data_period <- data_cleaned %>% mutate(number_of_periods = str_count(data_cleaned$ig_name, "\\."))

ggplot (data_period) +
  aes ( y = Followers, 
        x = number_of_periods) +
  geom_point()
```

```{r}
data_numbers <- data_cleaned %>% mutate(number_of_numbers = str_count(data_cleaned$ig_name, "\\d"))

ggplot (data_numbers) +
  aes ( y = Followers, 
        x = number_of_numbers) +
  geom_point()
```

```{r}
#contains_group_name <- str_detect(data_cleaned$ig_name, tolower(all_data_cleaned$Group))
#contains_group_name <- tibble(as.numeric(contains_group_name))

#Reformat names: 
#group_name_no_punctuations <- str_replace_all((all_data_cleaned$Group), "[[:punct:]]", "")

library(stringr)

data_texts <- data %>% mutate(
  
  contains_official = str_count(data$ig_name, "official"),
  contains_group_name = str_detect(data$ig_name, tolower(str_replace_all((data$Group), "[[:punct:]]", ""))),
  contains_stage_name = str_detect(data$ig_name, tolower(str_replace_all((data$Stage.Name), " ", "")))
 
   )

ggplot(data_texts) + 
  aes (x = Followers, y = contains_group_name, fill = contains_group_name, alpha = 0.5) +
  geom_boxplot(width = 0.4) +
  scale_x_continuous(trans='log2') +
  theme_dark() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "none") 


ggplot(data_texts) + 
  aes (x = Followers, 
      fill = contains_stage_name) +
  geom_histogram()




```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
