---
title: "Challenge-5"
author: "Nicole Lim"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE)
```

## Questions
<br>

#### Question-1: Local Variable Shadowing 

Create an R function that defines a global variable called `x` with a value of 5. Inside the function, declare a local variable also named `x` with a value of 10. Print the value of `x` both inside and outside the function to demonstrate shadowing.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
define_x <- function(x){
x <<- 5
x <- 10
print(x)
}

define_x(x)

print(x)

```
<br>

#### Question-2: Modify Global Variable

Create an R function that takes an argument and adds it to a global variable called `total`. Call the function multiple times with different arguments to accumulate the values in `total`.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
totaller <- function(initial = 0, amount_to_add, total) {
  
  total <- (initial + amount_to_add)
  total <<- total
  print(total)
  #initial <<- total
}

totaller(amount_to_add = 2)
totaller(initial = total, amount_to_add = 4)
totaller(initial = total, amount_to_add = 6)
print(total)
```
<br>

#### Question-3: Global and Local Interaction 

Write an R program that includes a global variable `total` with an initial value of 100. Create a function that takes an argument, adds it to `total`, and returns the updated `total`. Demonstrate how this function interacts with the global variable.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
totaller_2 <- function(total, number_to_add_2){
  
  total <<- 100
  total <- (total + number_to_add_2)
  print(total)
}

totaller_2 (total = total, number_to_add_2 = 27)

#This argument interacts with the global variable by drawing from its global value in the execution of the function.
```
<br>

#### Question-4: Nested Functions

Define a function `outer_function` that declares a local variable `x` with a value of 5. Inside `outer_function`, define another function `inner_function` that prints the value of `x`. Call both functions to show how the inner function accesses the variable from the outer function's scope.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
outer_function <- function(x){
  
  x <- 5
  inner_function <- function(x) print(x)
  inner_function(x)
}

outer_function(x)

```
<br>

#### Question-5: Meme Generator Function

Create a function that takes a text input and generates a humorous meme with the text overlaid on an image of your choice. You can use the `magick` package for image manipulation. You can find more details about the commands offered by the package, with some examples of annotating images here: https://cran.r-project.org/web/packages/magick/vignettes/intro.html

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
library(magick)
memeify <- function (meme_uppertext, meme_lowertext) {
  
  meme_image <- image_read("jingxiang2.jpeg")
  meme1 <- image_annotate(meme_image, meme_uppertext, size = 100, gravity = "north", color = "white", strokecolor = "black")
  meme2 <- image_annotate(meme1, meme_lowertext, size = 100, gravity = "south", color = "white", strokecolor = "black")
  print(meme2)
  
}

memeify("swag!", "BOTTOM TEXT")
```
<br>

#### Question-6: Text Analysis Game  

Develop a text analysis game in which the user inputs a sentence, and the R function provides statistics like the number of words, characters, and average word length. Reward the user with a "communication skill level" based on their input.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
suppressMessages(library("tidyverse"))
library(tidyverse)
library(magick)
sentencealyser <- function(sentence) {
  
  stats_tibble <- tibble( number_of_words = lengths(strsplit(sentence, " ")), characters = nchar(sentence), average_word_length = characters/number_of_words)
  
  #print(stats_tibble)
  
  number_of_words <- stats_tibble$number_of_words
  characters <- stats_tibble$characters
  average_word_length <- stats_tibble$average_word_length
  
  wordiness = case_when(number_of_words > 20 ~ 3, number_of_words > 10 ~ 2, number_of_words > 5 ~ 1, number_of_words < 5 ~ 0)
  characteriness = case_when(characters > 60 ~ 3, characters > 40 ~ 2, characters > 20 ~ 1, characters < 20 ~ 0)
  lengthiness = case_when(average_word_length > 8 ~ 3, average_word_length > 6 ~ 2, average_word_length > 4 ~ 1, average_word_length < 4 ~ 0)
  
  #print(characteriness)
  #print(wordiness)
  #print(lengthiness)
  
  eloquence = (characteriness + lengthiness + wordiness)
  
 # print(eloquence)
  
  comm_skill_level = case_when(eloquence > 7 ~ 3, eloquence > 4 ~ 2,  eloquence > 1  ~ 1, eloquence < 1  ~ 0, )
  
  replace_na(comm_skill_level, 0)
  
  congratulations <- paste0("Congratulations! Your communication skill level score is ", comm_skill_level, " out of 3!")
  medal <- image_read("medal.jpeg")
  medal_engraved <- image_annotate(medal, paste0("Skill Level: ", comm_skill_level), size = 30, gravity = "center", color = "black", location = "+0+50")
  
  print(congratulations)
  print(medal_engraved)
  
}

sentencealyser("It is a truth universally acknowledged, that a single man in possession of a good fortune, must be in want of a wife.")
```
<br>