---
pdf_document: default
author: "Nicole Lim"
date: "`r Sys.Date()`"
output:
  html_document: null
  df_print: paged
  pdf_document: default
title: "Week-5: Code-along"
---

  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# II. Code to edit and execute using the Code-along.Rmd file 
<br>

## A. Writing a function
<br>

### 1. Write a function to print a "Hello" message (Slide #14)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
print_hello <- function () { print("Hello")}

print_hello()

```
<br>

### 2. Function call with different input names (Slide #15)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
print_hello_to <- function (name) { print(paste0("Hello ", name, "!"))}

print_hello_to("RStudio")
print_hello_to("0_0")
```
<br>

### 3. typeof primitive functions (Slide #16)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
typeof(sum)
typeof(`+`)

```
<br>

### 4. typeof user-defined functions (Slide #17)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
typeof(mean)
typeof(print_hello_to)

```
<br>

### 5. Function to calculate mean of a sample (Slide #19)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
mean_of_sample <- function(samplesize) {
  mean(rnorm(samplesize))
  }
```
<br>

### 6. Test your function (Slide #22)

```{r, eval=TRUE,echo=TRUE}
# With one input
mean_of_sample(50)
```
<br>
```{r, eval=TRUE,echo=TRUE}
# With vector input
?rnorm
mean_of_sample(c(100,200,700))
```
<br>

### 7. Customizing the function to suit input (Slide #23)

```{r, eval=TRUE,echo=TRUE,message=FALSE}
# Enter code here
library(tidyverse)
sample_tibble <- tibble(samplesizes = c(100, 200, 700))
#*Tibble* is a list where all the columns have the same number of entries.
#*Group_by* groups by unique entries
#*Mutate* informs new column which has entries making use of previous function
sample_tibble %>% group_by(samplesizes) %>% mutate(samplemeans = mean_of_sample(samplesizes))
```
<br>

### 8. Setting defaults (Slide #25)

```{r, eval=TRUE,echo=TRUE}
# First define the function
calc_sample_mean <- function(samplesize,our_mean=0,our_sd=1) {
  
  sample <- rnorm(samplesize, mean = our_mean, sd = our_sd)
  
  mean(sample)
  
}
# Call the function 
calc_sample_mean(samplesize = 127)
```
<br>

### 9. Different input combinations (Slide #26)

```{r, eval=TRUE,echo=TRUE}
# Enter code here 
calc_sample_mean(127,115,15)
calc_sample_mean(4,12)
calc_sample_mean(99, our_mean = 12, our_sd = 2)
```
<br>

### 10. Different input combinations (Slide #27)

```{r, eval=TRUE,echo=TRUE,error=TRUE} 
# set error=TRUE to see the error message in the output
# Enter code here 
calc_sample_mean(our_mean=143)
```
<br>

### 11. Some more examples (Slide #28)

```{r, eval=TRUE,echo=TRUE,error=TRUE} 
# Enter code here 
plus_one <- function(x) x+1
plus_one(1)
plus_one("one")
plus_one(FALSE)
```
<br>

## B. Scoping
<br>

### 12. Multiple assignment of z (Slide #36)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
z <- 1
sprintf("The value assigned to z outside the function is %d", z)

```
<br>

### 13. Multiple assignment of z (Slide #37)

```{r, eval=TRUE,echo=TRUE}
# Enter code here
fn <- function( z = 2 ) {
  #Reassign z
  z <- 3
  return(z+3)
}

fn(z = 5)

sprintf("The final value of z after reassigning it to a different value inside of the function is %d", z)

#z accessed inside the function is using the value tree
#z accessed outside the function does not regard z inside the funciton
#scope defined by location of initialisation and where it can be accessed
#global scope = defined outside functions, accessed anywhere in the program
#local scope = declared inside functions, cannot be accessed outside of it
```
<br>